Who will win the US 2024 election?!!

### 2024-03-14 paper/paper.qmd
paper qmd file created- added the data section

# Introduction

>>>>

# Introduction
A key turning point in the political environment of the United States occurred with the 2022 presidential election,
which was marked by extreme conflict and serious economic and social challenges. We analyze data from the American
Community Survey (ACS) 2022 sample, which offers a thorough understanding of demographic, socioeconomic, and geographic
aspects across the nation, in order to comprehend the patterns underlying voting choices during this 2024 election
period.

Our estimand is the relationship between demographic, socio-economic, and geographic variables (such as age, income,
education, state of residence, and gender) and voting behavior during the 2022 presidential election. Using this
extensive dataset, our goal is to identify trends and factors that influence voting behaviour, clarifying the
complex relationship between personal traits and local factors that influences election results.

Our research adds to a greater understanding of the factors influencing voting decisions through comprehensive
statistical analysis, yielding insightful data that may influence future election campaigns and policy discussions.
Through highlighting the subtleties of voting patterns in the 2022 election, our research provides a critical insight
on the condition of American democracy and the factors motivating involvement in politics and engagement.
